HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex

\begin{table}
\begin{center}
\begin{tabular}{l|cccc}
& cs & de & pl & ro \\
\hline
Annot. 1 & 255 & 140  & 138 & 96 \\
Annot. 2 & -- & 162 & 229 & 207 \\
\end{tabular}
\caption{Median annotation times per sentence, in seconds.
We do not give times for the second Czech 
``annotator'', since this was a collection of annotators, working in parallel.}
\label{tab:annot_times}
\end{center}
\end{table}

\emph{Describe the UCCA annotation}

@@

@@

In order to assess the consistency of the annotation, we measure the Inter-Annotator
Agreement (IAA) using Cohen's Kappa on the multiply-annotated portions of the data.
For German, Polish and Romanian we used two annotators, with a significant overlap
between the sentences they annotated. For Czech we had one main annotator, who
annotated the entire batch, as well multiple secondary annotators, where
each annotated a sub-part of the batch. \oa{i editted it. is what i wrote correct?}

In order to compute Kappa, we consider the annotation task as a classification task on 
nodes, and compute agreement on nodes which have two annotations from different annotators.
We report the overall Kappa, as well as separate Kappas on atomic
nodes (annotated as Red, Orange or Green) and the structural nodes (annotated
as Adequate or Bad). In general there should be little confusion between the two
types of nodes, and in future work the separation between the nodes should be enforced
by the tool\oa{but there may be some disagreement in the margins on what nodes are atomic and
  what are not}. The Kappas are shown in \tabref{tab:iaa}.

\begin{table}[!ht]
\begin{center}
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & 181 & 102 & 334 & 217 \\
\hline
All nodes & 4686   & 2793   & 8384   & 5604  \\
Kappa & 0.64   & 0.61   & 0.58   & 0.69  \\
\hline
Atomic nodes & 2982 & 1724 & 5386 & 3570 \\
Kappa & 0.54 & 0.29 & 0.54 & 0.50 \\
\hline
Structural nodes & 1602 & 1040 & 2655 & 1989 \\
Kappa & 0.31 & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
\end{center}
\end{table}

>>>>

\begin{table}[t]
\begin{center}
\begin{tabular}{l|cccc}
& cs & de & pl & ro \\
\hline
Annot. 1 & 255 & 140  & 138 & 96 \\
Annot. 2 & -- & 162 & 229 & 207 \\
\end{tabular}
\caption{Median annotation times per sentence, in seconds.
We do not give times for the second Czech 
``annotator'', since this was a collection of annotators, working in parallel.}
\label{tab:annot_times}
\end{center}
\end{table}

%\XXX{Describe the UCCA annotation}
% ... not enough room or time

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & 181 & 102 & 334 & 217 \\
\hline
All nodes & 4686   & 2793   & 8384   & 5604  \\
Kappa & 0.64   & 0.61   & 0.58   & 0.69  \\
\hline
Atomic nodes & 2982 & 1724 & 5386 & 3570 \\
Kappa & 0.54 & 0.29 & 0.54 & 0.50 \\
\hline
Structural nodes & 1602 & 1040 & 2655 & 1989 \\
Kappa & 0.31 & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
\end{center}
\end{table}

@@

In order to assess the consistency of the annotation, we measure the Inter-Annotator
Agreement (IAA) using Cohen's Kappa on the multiply-annotated portions of the data.
For German, Polish and Romanian we used two annotators, with a significant overlap
between the sentences they annotated. For Czech we had the entire batch
annotated by one main annotator and multiple secondary annotators, 
each annotating a sub-part of the batch.

\tabref{tab:iaa} reports the number of nodes which have two annotations from
different annotators and the corresponding Kappas.
%
%In order to compute Kappa, we consider the annotation task as a classification task on 
%nodes, and compute agreement on nodes which have two annotations from different annotators.
We report the overall Kappa, as well as separate Kappas on atomic
nodes (annotated as Red, Orange or Green) and structural nodes (annotated
as Adequate or Bad).
As expected and confirmed by confusion matrices in \figref{fig:heatmap}, there
is generally little confusion between the two types of nodes.

%In general there should be little confusion between the two
%types of nodes, and in future work the separation between the nodes should be enforced
%by the tool.
%\oa{but there may be some disagreement in the margins on what nodes are atomic and
%  what are not}
%The Kappas are shown in \tabref{tab:iaa}.

\begin{figure}[t]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{cc}
